---
title: VSA Basic Model
author: Ross W. Gayler
date: |
  `r knitr::inline_expr('format(Sys.time(), "Updated on %A, %B %d, %Y %I:%M %p")')`
site: bookdown::bookdown_site
link-citations: true
bibliography: ./assets/refs.bib
csl: ./assets/apa.csl
---
---
title: VSA Basic Model
author: Ross W. Gayler
date: |
  `r knitr::inline_expr('format(Sys.time(), "Updated on %A, %B %d, %Y %I:%M %p")')`
site: bookdown::bookdown_site
link-citations: true
bibliography: ./assets/refs.bib
csl: ./assets/apa.csl
---



<!--chapter:end:index.Rmd-->

<!-- Chapters/posts are collated in reverse chronological order so  -->
<!-- this last one is a dummy entry to tell bookdown where to drop  -->
<!-- the references. -->

## References

<!--chapter:end:0000-00-00-references.Rmd-->

<!--- Timestamp to trigger book rebuilds: `r Sys.time()` --->

```{r setup, include = FALSE}
# library(tidyverse)
# fit <- targets::tar_read(fit)
# fit
```

## 2022-04-03 Design notes

<small>Source: <code>`r knitr::current_input()`</code></small>

This entry contains the VBM1 design notes.

As my design thinking evolves over the course of the project
the notes here will be modified
so that this note always reflects my most recent position.
Consequently the head date shouldn't be taken too seriously.

```{r content}

```

### Objectives

The purpose of the VSA Basic Model project is to develop a basic VSA model (VBM1),
as an alternative to HRR, FHRR, BSC, MAP, etc.,
which is conceptually simple as possible,
and relatively cheap computationally.
The motivation for this is that VBM1
would be the default VSA model for empirical projects,
that is, it would be the VSA equivalent of the geneticist's fruit fly.

### Design





<!--chapter:end:2022-04-03-design.Rmd-->

